Test data

### 2022-07-19 Shiny/Test/Flexdashboard rows.Rmd
Colours are driving me insane.

The KPIs are based on the following calculations

- **admin** is based on dividing
```{r}

>>>>

The KPIs are based on the following calculations:

- **admin** is based on dividing - expenses_administrative / expenses_program_services *100
- **Fundraising ROI** - (revenue_private_contributions +
                 revenue_membership_fees - expenses_fundraising) /
              expenses_fundraising * 100
```{r}

### 2022-07-19 Shiny/Test/Test data.Rmd
Colours are driving me insane.

>>>>

### Egenkapital og gjeld
```{r}
kreft_html2 <- kreft_html |> 
  mutate(
    profit = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
  )
kreft_html2 |> 
  ggplot(aes(year, sum_egenkapital_og_gjeld, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = label_dollar()) +
  scale_fill_met_d("Tsimshian",
                   direction = if (mean(kreft_html2$profit) == 1){-1} else {1})

kreft_html2 |> 
  ggplot(aes(year, sum_egenkapital_og_gjeld, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = label_dollar()) +
  scale_fill_met_d("Tsimshian",
                   direction = ifelse(mean(kreft_html2$profit) == 1,-1, 1))

# Need to add profit variables
